# Homework 1

This is a book created from markdown and executable code.

See @knuth84 for additional discussion of literate programming.

Favorite Graph
```{r}
x <- seq(-3,3,by=0.01)
y <- exp(x) + log(abs(x))
plot(x,y)
```
# Question 2
```{r}
# pak::pak("thomasgstewart/ds6021b")

require(ds6021b)

R1 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
plot(R1[,1], f1(R1), xlab = "x1", ylab = "y", type = "l")
legend("topleft", legend = "x2 = -0.5 & x3 = 0", box.lty = 0)

R2 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
plot(R2[,1], f2(R2), xlab = "x1", ylab = "y", type = "l")
legend("topleft", legend = "x2 = -0.5 & x3 = 0", box.lty = 0)

R3 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
plot(R3[,1], f3(R3), xlab = "x1", ylab = "y", type = "l")
legend("topleft", legend = "x2 = -0.5 & x3 = 0", box.lty = 0)

R4 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
plot(R4[,1], f4(R4), xlab = "x1", ylab = "y", type = "l")
legend("topleft", legend = "x2 = -0.5 & x3 = 0", box.lty = 0)

R5 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
plot(R5[,1], f5(R5), xlab = "x1", ylab = "y", type = "l")
legend("topleft", legend = "x2 = -0.5 & x3 = 0", box.lty = 0)
```

# Question 3
```{r}
R1_0 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
R1_1 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 1)
plot(R1_0[,1], f1(R1_0), xlab = "x1", ylab = "y", ylim = c(-1,4),type = "l")
lines(R1_1[,1], f1(R1_1), xlab = "x1", ylab = "y", type = "l", col = "red")
legend("topleft", legend = "x2 = -0.5 & x3 = 0 or 1", box.lty = 0)

R2_0 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
R2_1 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 1)
plot(R2_0[,1], f2(R2_0), xlab = "x1", ylab = "y", ylim = c(-1,4),type = "l")
lines(R2_1[,1], f2(R2_1), xlab = "x1", ylab = "y", type = "l", col = "red")
legend("topleft", legend = "x2 = -0.5 & x3 = 0 or 1", box.lty = 0)

R3_0 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
R3_1 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 1)
plot(R3_0[,1], f3(R3_0), xlab = "x1", ylab = "y", ylim = c(-1,4),type = "l")
lines(R3_1[,1], f3(R3_1), xlab = "x1", ylab = "y", type = "l", col = "red")
legend("topleft", legend = "x2 = -0.5 & x3 = 0 or 1", box.lty = 0)

R4_0 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
R4_1 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 1)
plot(R4_0[,1], f4(R4_0), xlab = "x1", ylab = "y", ylim = c(-1,4),type = "l")
lines(R4_1[,1], f4(R4_1), xlab = "x1", ylab = "y", type = "l", col = "red")
legend("topleft", legend = "x2 = -0.5 & x3 = 0 or 1", box.lty = 0)

R5_0 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 0)
R5_1 <- expand.grid(x1 = seq(-3,3,by=0.01), x2 = -0.5, x3 = 1)
plot(R5_0[,1], f5(R5_0), xlab = "x1", ylab = "y", ylim = c(-1,4),type = "l")
lines(R5_1[,1], f5(R5_1), xlab = "x1", ylab = "y", type = "l", col = "red")
legend("topleft", legend = "x2 = -0.5 & x3 = 0 or 1", box.lty = 0)
```

# Question 4

For the most part, a visual glance indicates that x3 with value 1 has higher y values than x3 with value 0. Although the results do vary in the final curve/outcome, the general shape of these plots are retained. 